Worflow

### 2017-06-07 R/workflow.Rmd
updated code to plotHeatmap

```{r}
sampleData <- data.frame(ours = primaryCluster(ceObj))
plotHeatmap(assays(se)$normalizedValues,
            main = 'Normalized values, 1000 most variable genes',
            clusterSamplesData = ceObj@dendro_samples,
            sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
```

>>>>

But an easier fix to the code would be to set `visualizeData` option. I haven't tested this because I don't have the objects need run, so let me know if there is error.

```{r}
# sampleData <- data.frame(ours = primaryCluster(ceObj))
# plotHeatmap(assays(se)$normalizedValues,
#             main = 'Normalized values, 1000 most variable genes',
#             clusterSamplesData = ceObj@dendro_samples,
#             sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
# easier fix:
plotHeatmap(ceObj, visualizeData=assays(se)$normalizedValues,
whichClusters="primary",
            main = 'Normalized values, 1000 most variable genes')

```
